% refer to https://github.com/jaredhoberock/personal/tree/master/doc/resume

\documentclass[margin,line]{res}

\usepackage{pdfpages}
\usepackage{hyperref}
\usepackage{url}
\usepackage{tikz}

\oddsidemargin=-0.5in
\evensidemargin=-0.5in
\textwidth=6.2in
\itemsep=0in
\parsep=0in

\def\checkmark{\tikz\fill[scale=0.4](0,.35) -- (.25,0) -- (1,.7) -- (.25,.15) -- cycle;} 

\newenvironment{list1}{
  \begin{list}{$\checkmark$}{
      \setlength{\parsep}{0in} \setlength{\parskip}{0.3cm}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0.3cm}
      \setlength{\leftmargin}{0.2in}}}{\end{list}}


\begin{document}

\name{WooKyoung Noh}

\begin{resume}

\vspace{-1.35cm}

\begin{flushright}
\begin{tabular}{@{}l|l}
\texttt{wookay.noh@gmail.com } & \texttt{ github.com/wookay} \\
\end{tabular}
\end{flushright}

\section{\sc Interests}
Julia (programing language)

\section{\sc Professional Experiences}

{\bf Woowa Brothers}, Seoul \hfill May 2014 - May 2015 \\
{\em Research Engineer} \\
Developed a web app for Japan-based food delivery service.

{\bf H2Soft}, Seoul \hfill Jul 2011 - Feb 2013 \\
{\em CTO} \\
Developed game development tools for mobile.

{\bf Shinhan BNP Paribas Asset Management Company}, Seoul \hfill Feb 2010 - Apr 2010 \\
{\em Lead Developer} \\
Developed a stock trading application for iOS.

{\bf Mintech}, Seoul \hfill Jul 2009 - Jan 2010 \\
{\em Research Engineer} \\
Developed the 3G network connection manager for Mac.

{\bf Orchard Party}, Seoul \hfill Oct 2008 - Jun 2009 \\
{\em Research Engineer} \\
Developed iOS games and toy apps.

{\bf Center for Youth and Cultural Studiees in Yonsei University}, Seoul \hfill Oct 2007 - Sep 2008 \\
{\em Research Engineer} \\
Developed a website for the students who attending alternative schools. \\
Research for community-based literacy learning.

{\bf Playforum}, Seoul \hfill Feb 2006 - Sep 2007 \\
{\em Research Engineer} \\
Developed websites for gaming community and trading in-game items.

{\bf Polypix}, Seoul \hfill Mar 2002 - Dec 2003 \\
{\em Research Engineer} \\
Developed an instant messenger for PC and PDA platform.

{\bf Web Data Bank}, Seoul \hfill Jul 2000 - Feb 2002 \\
{\em Research Engineer} \\
Developed the system for content delivery network (CDN) services.


\section{\sc Education}
{\bf Kyungsung University}, Busan \\
Bachelor of Science in Computer Engineering, February 2005


\section{\sc Publications}
{\bf Beautiful Julia Programming}\footnote{ Beautiful Julia Programming - \url{https://leanpub.com/bjp}} written in Korean, 2017


\section{\sc Selected Conference Presentations}
{\bf PushInterface.jl} - Interacting Julia with Electronic Musical Instrument\footnote{ PushInterface.jl, Poster Session at JuliaCon 2018, London - \url{https://juliacon2018.sched.com/event/FijE?iframe=no}} at JuliaCon 2018, London \hfill

{\bf Swifter.jl} - Scripting, REPL for iOS App Development\footnote{ Swifter.jl, presented at JuliaCon 2016, MIT - \url{https://www.youtube.com/watch?v=Jv1JQVQYm0I}} at JuliaCon 2016, MIT \hfill

\vspace{1.5cm}

\section{\sc Activities}

\vspace{-0.1cm}

\begin{list1}
\item A small contributor to Julia project
\end{list1}

\begin{list1}
\item Maintaining open source projects: \\
  {\bf Bukdu.jl}\footnote{ Bukdu.jl, a web development framework for Julia - \url{https://github.com/wookay/Bukdu.jl}}, a web development framework for Julia, 105 starred \hfill

  {\bf Octo.jl}\footnote{ Octo.jl, an SQL Query DSL in Julia - \url{https://github.com/wookay/Octo.jl}}, an SQL Query DSL in Julia, 85 starred \hfill

  {\bf Jive.jl}\footnote{ Jive.jl, some useful steps in tests - \url{https://github.com/wookay/Jive.jl}}, some useful steps in tests, 25 starred \hfill
\end{list1}

\begin{list1}
\item Organizing local developer community \\
  {\bf Julia Korea user group}\footnote{ Julia Korea user group - \url{https://facebook.com/groups/juliakorea}} since 2014
\end{list1}

\end{resume}

\end{document}
